Analysis of the inference of ratings and rankings on Higher Order Networks with complex topologies

### 2025-09-03 draft/draft.tex
progress

With each metric, a 1-cochain is defined as
$$
f_{ij}
=
\frac{1}{2}(m_{ij}+m_{ji})
$$
Moreover, in order to test the inference method, two types of ground-truth 1-cochains are also defined.
Namely, the rank-based 1-cochain $f_{ij}=\frac{1}{2}(i-j)$ and the tournament point 1-cochain $f_{ij}=\frac{1}{2}(\pi_j-\pi_i)$.
Note, $f_{ij}=-f_{ji}$ holds by definition.
These 1-cochains $f$ define a fully connected network or graph, since all pairs of teams play two matches against each other in each league.
Each of these fully connected graphs of $N=n+1$ nodes is promoted to a simplicial complex compose of 0-simplices labeled by $i$, 1-simplices labeled by $ij$ and 2-simplices labeled by $ijk$ where $i,j,k$ are different elements in $\{0,1,2,...,n\}$.

From a score $\phi$, a corresponding cochain $f\in C_1^*$ of coordinates $f_{ij}=\phi_{ji}-\phi_{ij}$ is defined.
Also, the cochain $f'\in C_1^*$ of coordinates $f'_{ij}=\phi_j-\phi_i$ with team strengths $\phi_i=\sum_j \phi_{ij}$ is considered.

>>>>

\subsection{Inference of ratings and rankings}

With each metric, the coefficients
$$
f_{ij}
=
\frac{1}{2}(m_{ij}+m_{ji})
$$
are defined for each $i$ and $j$ in $\{0,1,...,n\}$ such that $i<j$ and where $N=n+1$ is the number of teams in the corresponding league.
Moreover, in order to test the inference method, two types of ground-truth coefficients are also defined.
Namely, the rank-based coefficients $f_{ij}=i-j$ and the tournament points based coefficients $f_{ij}=\pi_j-\pi_i$.
These coefficients correspond to a fully connected network or graph with $N$ nodes since, as already mentioned, all pairs of teams play two matches against each other in each league.
Next, each fully connected graphs is promoted to a simplicial complex composed of 0-simplices labeled by $i$, 1-simplices labeled by $ij$ with $i<j$ and 2-simplices labeled by $ijk$ with $i<j<k$.
Finally, the coefficients $f_{ij}$ are promoted to be the components of a 1-cochain  $f$, where the anti-symmetric relation $f_{ji}=-f_{ij}$ must hold by definition.

%From a score $\phi$, a corresponding cochain $f\in C_1^*$ of coordinates $f_{ij}=\phi_{ji}-\phi_{ij}$ is defined.
%Also, the cochain $f'\in C_1^*$ of coordinates $f'_{ij}=\phi_j-\phi_i$ with team strengths $\phi_i=\sum_j \phi_{ij}$ is considered.

{\color{red}[JUAN: Write here the inference problem.]}
